\subsubsection*{Subproject IMG}

The research group GIBI230 is located and develops most of its work at the University and Polytechnic hospital La Fe, referral hospital in the Valencia community and one of the major hospitals in the Spanish territory, and especially at the Medical Imaging Clinical Area. 
This Medical Imaging Clinical Area has in one hand a Radiology Section with several CT devices (TC Brillance 64 Philips (2 devices), TC Brillance iCT 256 Philips, TC O-arm
Medtronic, TC Aquilion 64 Toshiba), densitometers (Discovery DXA Hologic) and X-RAY devices (Philips Digital Diagnost). On the other hand, in the Nuclear Medicine Section are available 3 SPECT/CT (Philips Brightview XCT) and a PET-CT device (Philips Gemini TF 64 with “TrueFlight” technology) the only PET/CT device in the public system of the Valencian Community.

Also the Medical Imaging Clinical Area (GIBI 230) boasts of Experimental Radiology Unit in which this project will be developed with a specific area of animals preparation annexed to the animal facility of the Institute for Health Research La Fe.

This space has a MRI device of 3T from Philips (Achieva 3.0T TX) specific to research. Jointly there is also a workstation for image processing Imalytics model (only 60 in the world), product of Philips Healthcare for their reference research centers. For the projects of the group there is also space in the hospital PACS dedicated to research, in which free space will be allocated by AGFA for storing images, thanks to a Master Research Agreement between this company and the hospital for the development of innovative projects in medical imaging.

\subsubsection*{Co-funding proposal}
 This project does not require equipment co-funding. 
